Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-06 Paper/Poster/poster.tex
bib added

@@

%%% References
\bibliographystyle{IEEEtran}
\bibliography{refs.bib}

@@

% FOOTNOTE
%\vspace{10cm}
\begin{minipage}{\textwidth}
\begin{flushright}
Poster presented at ISMIR 2010 (Utrecht) for the paper:
Clustering Beat-Chroma Patterns in a Large Music Database by
T. Bertin-Mahieux, R. J. Weiss and D. P. W. Ellis. Contact:
\url{tb2332@columbia.edu}, code: \url{http://www.columbia.edu/~tb2332/}.
\end{flushright}
\end{minipage}

>>>>

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Availability of very large collections of music audio:
can we infer anything about the underlying structure and common
features of e.g. commercial pop music?
\item Our interest: tonal content of the music -- i.e. the
harmony and melody.
\item Beat-synchronous chromagrams: rich enough
to generate musically-relevant results, simplified enough to
abstract away instrumentation and other stylistic details.
\item This paper identifies common patterns in beat-synchronous
chromagrams by learning codebooks from a large set of examples.
The individual codewords consist of short beat-chroma patches of
between 1 and 8 beats, optionally aligned to bar boundaries.
\end{list}

\myfig[0]{code_axis.ps}{.2}

%
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Goal: identify meaningful information
about the musical structure represented in the entire database by
examining individual entries in this codebook.
\item Prior work: ``shingles'' of \cite{Casey2007}, 
beat-synchronous analysis to indeitfy the chorus by \cite{Bartsch2001},
and cover recognition by \cite{Ellis2007a}.
\end{list}

@@

%%% References
\bibliographystyle{IEEEtran}
\bibliography{tbm_bib}

@@

% FOOTNOTE
\vspace{1cm}
\begin{minipage}{\textwidth}
\begin{small}
\begin{flushright}
Poster presented at ISMIR 2010 (Utrecht) for the paper:
Clustering Beat-Chroma Patterns in a Large Music Database by
T. Bertin-Mahieux, R. J. Weiss and D. P. W. Ellis. Contact:
\url{tb2332@columbia.edu}, code: \url{http://www.columbia.edu/~tb2332/}.
\end{flushright}
\end{small}
\end{minipage}
